Stability concerns in random matrices

### 2018-04-08 random_matrix_stability.Rmd
New results and manuscript start

@@

>>>>

**New result -- a correlation between the number of positive or negative values in a row of the Jacobian matrix (e.g., corresponding to a species that is generally positively affected by increases in other species -- generalist predator, or generally negatively affected by increases in other species -- a producer or resource), and the response rate of that row (e.g., species generation), is *highly* stabilising, and I believe that I can dig into the matrices and show that *this* is the mechanism that is tweaked when $Var(\gamma_{i})$ is included. In other words, variation in generation time inevitably increases or decreases the correlation (from zero) between sum of row signs and *types* of interactions and generation time -- which I will now generalise to something like reaction rate.** I will present these results in figures soon. I will also show that 1. general variation in $\gamma_{i}$ changes the correlation between sign counts and generation rate and 2. when this correlation is higher or lower, eigen values are more likely to all be negative.

@@

**Here's the correlation codes:**

```{r, eval = FALSE}
SA1      <- sign(A1);
Sadj     <- apply(X = SA1, MARGIN = 1, FUN = sum);
mnadj    <- 1 - min(Sadj);
Sadj     <- exp(Sadj + mnadj);
```

The above is saved as `random_pos.csv`. The rate of change $\gamma_{i}$ in row $i$ equals the sum values in the row, plus the minimum number of values (e.g., four positive and three negative value equals one, plus whatever is the minimum -- if -3, then the end value should be four).

```{r, eval = FALSE}
SA1      <- sign(A1);
Sadj     <- apply(X = -SA1, MARGIN = 1, FUN = sum);
mnadj    <- 1 - min(Sadj);
Sadj     <- exp(Sadj + mnadj);
```

The above is saved as `random_neg.csv`. The rate of change $\gamma_{i}$ in row $i$ equals the opposite of the sum values in the row, plus the minimum number of values.
